\section{What is deep learning?}
Deep Learning is a subfield of Machine Learning that is inspired by the structure and function of the human brain, known as neural networks. It involves the use of artificial neural networks with multiple layers to learn from data and perform complex tasks like image and speech recognition, natural language processing, and autonomous decision-making.

Deep Learning is called "deep" because it involves training neural networks with many layers, which are called deep neural networks. The idea is to stack multiple layers of simple processing units called artificial neurons to form a complex, hierarchical model that can represent highly abstract and non-linear relationships between input and output data.

Deep Learning has revolutionized many fields like computer vision, natural language processing, and speech recognition, and it is now used in many industries like healthcare, finance, and transportation. Some popular Deep Learning architectures are Convolutional Neural Networks (CNNs), Recurrent Neural Networks (RNNs), Generative Adversarial Networks (GANs), and Transformers.

One of the key benefits of Deep Learning is its ability to automatically learn useful features and representations from raw data without the need for human intervention or feature engineering. This has enabled Deep Learning models to achieve state-of-the-art performance on many complex tasks, outperforming traditional machine learning models and even human experts in some cases.

Overall, Deep Learning is a powerful technology with the potential to transform many industries and improve our daily lives.

