\section{What is the difference between supervised and reinforcement learning?}
Supervised learning and reinforcement learning are two different types of machine learning.

Supervised learning is a type of machine learning where the algorithm is given a set of labeled input-output pairs (i.e., training data) and learns to map new inputs to their corresponding outputs. The goal of supervised learning is to learn a general mapping function that can accurately predict the output for new, unseen inputs. The training process involves adjusting the parameters of the model to minimize the difference between the predicted output and the true output.

Reinforcement learning, on the other hand, is a type of machine learning where an agent learns to make a sequence of decisions in an uncertain, dynamic environment to maximize a cumulative reward signal. The agent interacts with the environment, receiving feedback in the form of a reward signal for each action it takes. The goal of reinforcement learning is to learn a policy (i.e., a mapping from states to actions) that maximizes the expected cumulative reward over time. The training process involves exploring the environment, selecting actions, and updating the policy based on the observed rewards.

In summary, supervised learning is used for problems where the correct output is known for each input, while reinforcement learning is used for problems where the correct output is not known, but the agent must learn to make a sequence of decisions to maximize a cumulative reward signal.

